Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
restructuring sections.

@@

To describe evidences for developers, we can use Hspec.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences as user documentation}
\label{sec:for-users}

@@

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences as code documentation (TBD: Is this still
appropriate here?}
\label{sec:for-developers}

\begin{quote}
    \emph{TBD: Behavior should be replaced with evidences in this subsection?}
\end{quote}

If we have evidence that does not fit into the user documentation, but would
rather be part of a design document, we use Hspec.

Hspec provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.

\noindent The {\tt it} function combines a text description for a behavior and
an evidence that gives some confidence in that behavior into a
spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties inot a \texttt{Property}.

\begin{quote}
    \emph{TBD: provide an example?}
\end{quote}

A spec can be run with the \texttt{hspec} function.  When a spec is run, all
evidences are evaluated, and failing evidences are
reported to the user (FIXME: user does not fit our definition of \emph{user}
here!).

\begin{quote}
    \emph{TBD: should user be replaced with developer?}
\end{quote}

\subsection{Setting expectations}

@@

\subsubsection{Expecting exceptions}

@@

\subsection{\emph{optional} Automatic discovery of specs}
TBD

>>>>

\subsection{Doctest and Haddock}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hspec}

To describe evidences for developers, we can use Hspec.
Hspec provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.

\noindent The {\tt it} function combines a text description and
an evidence and makes a spec.
Examples can be arbitrary HUnit assertions.  Properties must be of type {\tt
Property}; QuickCheck's \texttt{property} function can be used to turn
arbitrary properties into a \texttt{Property}.

A spec can be run with the \texttt{hspec} function.  When a spec is run, all
evidences are evaluated, and failing evidences are reported to developers.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Problem Summary}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences for users}
\label{sec:for-users}

@@

%%%%%%%%%%%%%%%%
\subsubsection{Markup for Examples}

@@

%%%%%%%%%%%%%%%%
\subsubsection{Markup for Properties}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evidences for developers}

We propose following extensions for Hspec to 
describe evidences for developers.

%%%%%%%%%%%%%%%%
\subsubsection{Setting expectations}

@@

%%%%%%%%%%%%%%%%
\subsubsection{Expecting exceptions}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\emph{optional} Automatic discovery of specs}
TBD
